State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-27 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
equation 17 correction adding t+1
equation 15 correction multiplying zeta by sampling time
equation 17 correction multiplying zeta by sampling time
paper updates

%<-comment out this for checking equations (author list too)
\usepackage{iopams,setstack}

%<-comment out this for checking equations
\usepackage{graphicx,epsfig}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}

%\renewcommand{\subcapsize}{\small}
% \usepackage{anysize}							%<-use this for checking equation length
% \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
% \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
% \usepackage{amsmath,amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

\section{Introduction} This paper presents a framework for creating patient specific macroscopic neural field continuum mathematical models. \todo{I think it's probably good to start like this, but there either needs to be more here or this needs to be folded into the following paragraph. Otherwise this first sentence looks a little out of place.}

@@

	\label{DefKernelDecomp} w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\theta}^{\top} \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right). 

@@

The spatial frequency of the observations is shown in figure~\ref{}. The peak power of the spatial frequency of the observations was approximately $30$~dB. The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB. This provided a conservative The oversampling parameter $\rho=2$. From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion. \todo{maybe from Parham's derivation... From equation~\ref{} the width was calculated to be... or...}. The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
\begin{figure*}
	\begin{center}
		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
	\end{center}
	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
\end{figure*}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.

>>>>

%<-comment out this for checking equations (author list too)
\usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx,epsfig}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}
\usepackage{pstool}
%\renewcommand{\subcapsize}{\small}
% \usepackage{anysize}							%<-use this for checking equation length
% \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
% \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
% \usepackage{amsmath,amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

\section{Introduction} This paper presents a theoretical framework for estimating patient specific macroscopic neural field continuum mathematical models from data. The ability to estimate such models has the potential to have significant impact on several areas of neuroscientific research and clinical neurology. Specifically, the development of a patient-specific state-space model will allow for the application of systems theoretical techniques from engineering to be applied to neuro-dynamics. For example, state tracking could be used in brain-computer interface or epileptic seizure prediction applications, where specific regions of the state-space may indicate intent of movement or imminent seizures. In addition, a patient specific state-space model will allow application of control engineering techniques to robustly prevent the neuro-dynamics entering pathological regions of state-space using electrical stimulation.

In addition, parameter estimation may have significant impact on the treatment of disease. For example, recent theoretical work has demonstrated that seemingly similar electrographic seizures in absence epilepsy may arise from abnormal excitatory or inhibitory mechanisms \omg{(ref, Frank Marten)}. These very different mechanisms would require very different medications for successful treatment. However, the underlying mechanisms would be hidden from the clinician in the normal clinical setting. Successful parameter estimation has the potential to reveal these hidden mechanisms allowing for improved treatment strategies. \omg{I extended this bit I am not sure how to connect it with the rest.} \todo{I think it's probably good to start like this, but there either needs to be more here or this needs to be folded into the following paragraph. Otherwise this first sentence looks a little out of place.}

@@

	\label{DefKernelDecomp} w\left(\mathbf{r}-\mathbf{r}'\right) = \boldsymbol{\psi}\left(\mathbf{r}-\mathbf{r}'\right)^{\top} \boldsymbol{\theta}

@@

The spatial frequency of the observations is shown in figure~\ref{}. The peak power of the spatial frequency of the observations was approximately $30$~dB. The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB. This provided a conservative The oversampling parameter $\rho=2$. From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion. \todo{maybe from Parham's derivation... From equation~\ref{} the width was calculated to be... or...}. The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.

\psfragfig{./Graph/FreqAnalysis}

% \begin{figure*}
% 	\begin{center}
% 		\include{FreqAnalysis.tex}
% 		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
% 	\end{center}
% 	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:FreqAnalysis} 
% \end{figure*}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.
